The Country-level Impact of Educational Patterns on the Rate of Entrepreneurship

### 2014-10-21 EducProposal.Rmd
Update EducProposal.Rmd

####Estimation Strategy  
The estimation strategy will consist of using cross-sectional data about Sweden, France and Britain at different points in time regarding the sense of belonging to a group, self-confidence patterns and the entrepreneurship features of each country.

>>>>

####Estimation Strategy  
The estimation strategy will consist of using cross-sectional data about Portugal, Sweden, France and Britain at different points in time regarding the sense of belonging to a group, self-confidence patterns and the entrepreneurship features of each country.
